---
title: "EHR-STI survey"
author: "Epiconcept"
date: "`r Sys.Date()`"
output:
  word_document:
    reference_docx: "template/ECDC_template.docx"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

\

\

```{r}
tab_status
```

\newpage

```{r, results='asis'}
cat('\n\n```{=openxml}\n<w:p><w:pPr><w:sectPr><w:pgSz w:w="11906" w:h="16838"/></w:sectPr></w:pPr></w:p>\n```\n\n')
```


**For the healthcare services listed below, are there EHR/EMR systems for gonococcal infection that could be employed for this EHR project?**


```{r}
tab_main
```

*For Hospitals, Laboratories and Other services, please specify the services:*
 
```{r}
tab_mainspespe
```
\
```{r}
tab_use
```
\
```{r}
tab_freq
```
\
```{r}
tab_cov
```
\
```{r}
tab_covm
```
\
```{r}
tab_covmi
```
\
```{r}
tab_prop
```

\newpage

**4. Are the variables below collected and stored in a structured way (e.g., no free text but instead dropdown menus / coded values, numeric, etc)**

```{r}
tab_agesex
```
\
```{r}
tab_agesexcomp
```

\newpage

```{r}
tab_symptoms
```
\

```{r}
tab_symptomscomp
```

\newpage

```{r}
tab_siteinfection
```
\

```{r}
tab_siteinfectioncomp
```

\newpage

```{r}
tab_labconf
```
\

```{r}
tab_labconfcomp
```

\newpage

```{r}
tab_amr
```
\

```{r}
tab_amrcomp
```

\newpage

```{r}
tab_transmission
```
\

```{r}
tab_transmissioncomp
```

\newpage

```{r}
tab_hiv
```
\

```{r}
tab_hivcomp
```

\newpage

```{r}
tab_pregnancy
```
\

```{r}
tab_pregnancycomp
```
\

```{r}
tab_clinlab
```

\newpage

6. Please describe any obstacles and limitations you may foresee in **accessing** this electronic health data on gonorrhea and using it for surveillance purposes (e.g., ethical issues, legal issues, technical capacity, resources etc)

```{r}
tab_speobstacleassessing
```

```{r}
tab_hosobstacleassessing
```

```{r}
tab_phobstacleassessing
```

```{r}
tab_privobstacleassessing
```

```{r}
tab_onlobstacleassessing
```

```{r}
tab_labobstacleassessing
```

```{r}
tab_othobstacleassessing
```

\newpage

7. Please describe any obstacles and limitations you may foresee in **reporting** this electronic health data on gonorrhoea for surveillance purposes at European level (e.g., ethical issues, legal issues, technical capacity, resources etc)

```{r}
tab_speobstaclereporting
```

```{r}
tab_hosobstaclereporting
```

```{r}
tab_phobstaclereporting
```

```{r}
tab_privobstaclereporting
```

```{r}
tab_onlobstaclereporting
```

```{r}
tab_labobstaclereporting
```

```{r}
tab_othobstaclereporting
```


\newpage

*Any comment related to the data sources of interest?*

```{r, eval=FALSE}
tab_comment
```

```{r}
tab_specomment
```

```{r}
tab_hoscomment
```

```{r}
tab_phcomment
```

```{r}
tab_privcomment
```

```{r}
tab_onlcomment
```

```{r}
tab_labcomment
```

```{r}
tab_othcomment
```

\newpage

**Any comment related to the survey?**

```{r}
tab_final
```

```{r, results='asis'}
cat('\n\n```{=openxml}\n<w:p><w:pPr><w:sectPr><w:pgSz w:w="16838" w:h="11906" w:orient="landscape"/></w:sectPr></w:pPr></w:p>\n```\n\n')
```
